\Title

### 2023-06-14 Grimaldi-etal-BiolCybernetics.tex
Update Grimaldi-etal-BiolCybernetics.tex

The response of a biological neuron depends on the precise timing of spikes from afferent neurons. This temporal aspect of the neural code is essential for understanding information processing in neurobiology, and is particularly applicable to the output of neuromorphic hardware such as event-based cameras. However, most artificial neural models do not take advantage of this important temporal dimension of the neural code. Here, we develop a model for the efficient detection of temporal spiking motifs based on a layer of spiking neurons with heterogeneous synaptic delays. The model takes advantage of the property that the diversity of synaptic delays on the dendritic tree allows for the synchronization of specific arrangements of synaptic inputs as they reach the basal dendritic tree. We show that this can be formalized as a time-invariant logistic regression that can be trained on labeled data. We demonstrate its application to synthetic naturalistic videos transformed into event streams similar to the output of the retina or event-based cameras. In order to characterize the robustness of the model in detecting visual motion, we test its efficiency by pruning some weights and show it is still efficient at very low workloads. In conclusion, heterogeneous delays provide an end-to-end event-driven computational building block which could improve the performance of future spiking neural network (SNN) algorithms and in particular their applications in neuromorphic chips.

>>>>

The response of a biological neuron depends on the precise timing of spikes from afferent neurons. This temporal aspect of the neural code is essential for understanding information processing in neurobiology, and is particularly applicable to the output of neuromorphic hardware such as event-based cameras. However, most artificial neural models do not take advantage of this important temporal dimension of the neural code. Here, we develop a model for the efficient detection of temporal spiking motifs based on a layer of spiking neurons with heterogeneous synaptic delays. The model takes advantage of the property that the diversity of synaptic delays on the dendritic tree allows for the synchronization of specific arrangements of temporally precise synaptic inputs as they reach the basal dendritic tree. We show that this process can be formalized as a time-invariant logistic regression that can be trained on labeled data. We demonstrate its application to  naturalistic videos transformed into event streams similar to the output of the retina or event-based cameras. In order to characterize the robustness of the model in detecting visual motion, we test its efficiency by pruning some weights and show it is still efficient at very low workloads. In conclusion, heterogeneous delays provide an end-to-end event-driven computational building block which could improve the performance of future spiking neural network (SNN) algorithms and in particular their applications in neuromorphic chips.
